Formal Paper Draft

### 2022-01-12 PaperDraft.Rmd
Adding updates for sammon with one grup

mds1 <- readRDS("2021-10-20_simulationNoInfluence_mds_list.RDS")
tsne1 <- readRDS("2021-10-20_simulationNoInfluence_tsne_list.RDS")

@@

@@

#mean detection rates
Category <- c("Correctly Identified Influential", "Correctly Non-Identified Non-Influential")
TSNE <- c(round(mean(ci1),3), round(mean(cni1),3))
MDS <- c(round(mean(ci2),3), round(mean(cni2),3))
Isomap <- c("","")
Sammon <- c("","")
temp <-rbind(Category,TSNE, MDS, Isomap, Sammon)
colnames(temp) <- Category
kable(temp)

>>>>

mds1 <- readRDS("2021-10-20_simulationNoInfluence_mds_list.RDS")
tsne1 <- readRDS("2021-10-20_simulationNoInfluence_tsne_list.RDS")
sammon1 <- readRDS("2022-01-11_simulationNoInfluence_Sammon_list.RDS")

@@

#### Generate a table of values to assess efficacy of detections -----------------#
df2list <- tsne1
df3list  <- mds1
df4list <- sammon1
#note - these will give values per run - so we need to take a look across the simulations

@@

#Sammon
ci3 <- sapply(df4list, spuriousInfluence)
cni3 <- 1 - ci3

#mean detection rates
Category <- c("Correctly Identified Influential", "Correctly Non-Identified Non-Influential")
TSNE <- c(round(mean(ci1),3), round(mean(cni1),3))
MDS <- c(round(mean(ci2),3), round(mean(cni2),3))
Isomap <- c("","")
Sammon <- c(round(mean(ci3),3),round(mean(cni2),3))
temp <-rbind(Category,TSNE, MDS, Isomap, Sammon)
colnames(temp) <- Category
kable(temp)
